---
title:    |
          | Empirical problem set
          | BUS456 Fall 2022
author: |
        | Group 12
        | Ekaterina Poruchikova - s222650
        | Jhih-Jiuan Cheng - s222648
        | Shuta Yamada - s222422
date: "`r Sys.Date()`"
output: pdf_document
---

\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, echo = FALSE, message = FALSE}
library(stargazer) # Pretty statistics output
library(purrr) # Iterations
library(dplyr) 
library(scales) # Turn decimals in %
library(vtable) # p.vals
library(pROC) # AUC
library(caret) # ConfusionMatrix
```



```{r, echo = FALSE}
setwd('C:/Users/steef/Documents/NHH/BUS456 Behavioral Business Strategy/BUS456-Assignment-1')

# Read the file
auto <- read.csv('automated_anonymous.csv')
```

# Question 1

Table 1 shows the frequency of the claimcolour: Green claim is 5674, Red is 1492, Yellow is 13190. Table 2 presents the the insurance type, where auto is 7562, life is 2305, other is 35, property is 5865, travel is 4589.

```{r question-1, echo = FALSE}
# Transform to factor variables
claiminternalnumber <- as.data.frame(auto[, 1])
names(claiminternalnumber)[names(claiminternalnumber) == 'auto[, 1]'] <-
  'claiminternalnumber'

auto[, -1] %>%
  map(as.factor) %>%
  cbind(claiminternalnumber, .) -> auto
rm(claiminternalnumber)

knitr::kable(t(table(auto$claimcolour)),
             caption = 'Frequency of the claim colour') %>%
  kable_styling(latex_options = 'hold_position')  

knitr::kable(t(table(auto$insurancetype)),
             caption = 'Frequency of the insurance type') %>%
  kable_styling(latex_options = 'hold_position')  

# Find insurance claims with empty insurance types
empty.insurance.type <-
  which(auto$insurancetype == '', arr.ind = TRUE)
print(paste(
  'Insurance claim with empty insurance type:',
  empty.insurance.type
))

# Remove these observations from the sample
auto <- auto[-c(17857, 18515), ]
```


# Question 2

Table 3 presents the fraction of claims by colour, while Table 4 provides the breakdown by claim colour and insurance type. In the green claim color other has the highest share, while the second largest category is property insurance. In the yellow category most prominent are life and travel insurance policies. At the same time red claim color is most common in the travel category. However, the travel has the lowest green claim color, other and property have two of the lowest values in yellow category, while auto has the lowest value in red. Therefore it can be concluded that travel is the least likely category to be suitable for automatic evaluation.



```{r question-2, echo = FALSE}
auto$green <- ifelse(auto$claimcolour == 'Green', 1, 0)
auto$yellow <- ifelse(auto$claimcolour == 'Yellow', 1, 0)
auto$red <- ifelse(auto$claimcolour == 'Red', 1, 0)

auto %>% 
  summarise(
    green = mean(green),
    yellow = mean(yellow),
    red = mean(red)
  ) %>%
  knitr::kable(caption = 'Percentage of claim color') %>%
  kable_styling(latex_options = 'hold_position')

auto %>% 
  group_by(insurancetype) %>%
  summarise(
    green = mean(green),
    yellow = mean(yellow),
    red = mean(red)
  ) %>%
  knitr::kable(caption = 'Percentage of claim color by insurance type') %>%
  kable_styling(latex_options = 'hold_position')

```

# Question 3

When we look at the results of the statistical test in the Table 5, only four treatment variables and “privatefinanced” are statistically significant. Therefore we can say that the groups are well randomized (balanced) in terms of the other variables. 
As to the four treatment variables, it is natural that the means of variables are statistically different between groups. They are designed to take the form of 1 in a certain treatment group, and take the form of 0 in all the other groups. Therefore, the mean will be 1 in one specific group, and 0 in the other groups, which will be considered a big difference. However, this is the intended result, so we can ignore these variables when we think about whether our groups are well-balanced or not.
The only variable to be considered in the analysis is “privatefinanced.” We need to control this variable when we run regressions. 
Overall, we can take away from the balance table that treatment groups and the control group are well balanced in terms of variables, and they will not be likely to cause problems in the following analysis except "privatefinanced."

```{r question-3, echo = FALSE, results='asis'}
auto %>% 
  select(-c(green, yellow, red, accept_automatic)) %>% 
  sumtable(group = "treatmentgroup", 
           summ = list(c('notNA(x)','mean(x)')),
           summ.names = list(c('N','Mean')), 
           group.test = T, out = 'latex',
           title = 'Balance table')
```

# Question 4

Table 6 presents the regression output. In the first model the constant term is positive and statistically significant (at 1% level). From this result, we can estimate that without treatments, customers have a general tendency to accept automated claim procedures. If we think about the fact that over 80% of customers have either green or yellow claim color, this result makes intuitive sense.
All treatment variables have positive coefficients. However, among four treatment variables, only social norm treatment and combined treatment are statistically significant. The P-value of social norm treatment is below 5% significance level, and that of combined treatment is below 1% level. In terms of the result of social norm treatment, it aligns with the theory of reciprocity (conditional cooperation). Although customers cannot observe how other customers behave in this experiment, the information about others’ pro-social behaviors (accepting automated procedures) might have affected their choices.
As to combined treatment, it has a larger coefficient than the social norm treatment. In addition to the effects of social norm treatment, simplification might reduce the cognitive efforts of customers and contribute to increase the rate of acceptance.


```{r question-4, echo = FALSE}
# Create 4 dummy variables
auto$simplification <-
  ifelse(as.character(auto$treatmentgroup) == '1', 1, 0)
auto$personalization <-
  ifelse(as.character(auto$treatmentgroup) == '2', 1, 0)
auto$social.norm <-
  ifelse(as.character(auto$treatmentgroup) == '3', 1, 0)
auto$combined <-
  ifelse(as.character(auto$treatmentgroup) == '4', 1, 0)

auto$accept_automatic <-
  as.numeric(as.character(auto$accept_automatic))

linear.model <-
  lm(accept_automatic ~ simplification + personalization +
       social.norm + combined,
     auto)
```

# Question 5

In the second regression in the Table 6, the coefficient of the variable “privatefinanced” is negative and statistically significant (1% level). Thus, we can assume that there is a negative correlation between paying expenses on insurance from a personal budget and accepting automated procedures. 
This can be backed up by Prospect Theory. Since the value function is steeper in the loss domain than in the gain domain, it is difficult for customers paying insurance fees by themselves (loss), to be driven by the utility from being “good” (gain from pro-social behavior, accepting automation). 
The change in the social norm group coefficient and its significance can most likely be attributed to a random chance as the sign of the coefficient remains the same and the value of the coefficient decreased only slightly and p-value changed from 3% to 5%. Therefore, the interpretation would not change drastically. 

```{r question-5, echo = FALSE, results='asis'}
linear.model.w.controls <-
  lm(accept_automatic ~ simplification + personalization + social.norm + 
       combined + insurancetype + red + green + privatefinanced, auto)
stargazer(linear.model, linear.model.w.controls, header = FALSE,
          title = 'Regression output')

summary(linear.model) -> lms
summary(linear.model.w.controls) -> lmwcs

print(paste('p-value of social.norm, model 1:',lms$coefficients[[19]]))
print(paste('p-value of social.norm, model 2:',lmwcs$coefficients[[40]]))
```

# Question 6

In the Table 7 separate regressions by claim color are presented. 
Combined treatment had the largest effect on the group with the “Yellow” claim color.
Also, the coefficient is only statistically significant for this group (1% level). 
However, this might not be the very result the company wanted, because claims labeled “Yellow” require some elements of personal evaluation. 
Although they can expect an increase in operational/financial efficiency from automation, the effect would not be as big as they expected. They will still need humans to process these claims and the time spent on procedures might not change so significantly. This may damage customer experiences because it kills one of the good features of automated claim procedures for customers. Since automation leads to a reduction of time for procedures, it is natural for customers who accept it to expect getting answers for their claims in a shorter time. This would shift their reference point to evaluate time spent on the procedures: for example, from setting 2-3 days as the origin (reference point) to setting 1 day or several hours as the origin. However, it would take longer than 1 day or several hours if their claims are not very suitable for automation, of which the claim color is “Yellow.” This will not be a problem for customers with the former reference point, but for those who with the latter reference point, it is interpreted as a loss. This will degrade customer experiences and ultimately, may lead to the unwanted result, the loss of customers.


```{r question-6, echo = FALSE, results='asis'}
auto %>%
  filter(treatmentgroup == 0 | treatmentgroup == 4) %>%
  filter(claimcolour == 'Green') %>%
  lm(accept_automatic ~ combined, .) -> model.green

auto %>%
  filter(treatmentgroup == 0 | treatmentgroup == 4) %>%
  filter(claimcolour == 'Yellow') %>%
  lm(accept_automatic ~ combined, .) -> model.yellow

auto %>%
  filter(treatmentgroup == 0 | treatmentgroup == 4) %>%
  filter(claimcolour == 'Red') %>%
  lm(accept_automatic ~ combined, .) -> model.red

stargazer(model.green, model.yellow, model.red, header = FALSE, 
          column.labels = c('Green', 'Yellow', 'Red'),
          title = 'Regressions by claim color')
```

# Question 7

As an additional analysis we ran a logistic regression to predict the automatic acceptance. The results of the regression are presented in the Table 8. The same variables as in the linear regression in Table 6 were found significant. However, due to larger presentce of automatic asseptances in the sample, as demonstrated by Table 9, the predictions made by the model were exclusively automatic acceptances. Therefore the model accuracy suffered, as demonstrated by the ROC figure. 

```{r question-7, echo = FALSE, results='asis'}
# Transform to factors 
auto$accept_automatic <- as.factor(auto$accept_automatic)

# Logit regression
logit.model <- glm(accept_automatic ~ simplification + personalization + social.norm + 
       combined + insurancetype + red + green + privatefinanced, auto, 
                   family = 'binomial')

stargazer(logit.model, header = FALSE, 
          title = 'Logistic regression output')

predicted <- predict(logit.model, auto, type = 'response')
test_roc = roc(auto$accept_automatic ~ predicted, plot = TRUE, print.auc = TRUE)


knitr::kable(table(auto$accept_automatic),
             caption = 'Summary statistics of the logit predictions') %>%
  kable_styling(latex_options = 'hold_position') 

print(paste('Lowest probability prediction is',round(min(predicted),2)))
```
